---
title: "environment_variables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{environment_variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lacrmr)
```


# Why using lacrmr?

lacrmr is a package that allows you to connect with your [Less Annoying CRM](https://www.lessannoyingcrm.com/) account and obtain the data of your
customers and contacts.

# What information can we obtain with lacrmr

The lacrmr package have four functions:

- `get_pipeline_report()`
- `search_contacts()`
- `get_contact_information()`
- `get_account_information()`

**`get_pipeline_report()`**

This function returns the data from one specific pipeline that you create
on your CRM. For this you will need to obtain the pipeline id that you want
to work with from R.

The variables to obtain with this function are:

```
 [1] "result_contact_id"                           
 [2] "result_user_id"                              
 [3] "result_company_id"                           
 [4] "result_background_info"                      
 [5] "result_birthday"                             
 [6] "result_is_company"                           
 [7] "result_company_name"                         
 [8] "result_industry"                             
 [9] "result_num_employees"                        
[10] "result_creation_date"                        
[11] "result_edited_date"                          
[12] "result_original_google_id"                   
[13] "result_employer_name"                        
[14] "result_company_employees"                    
[15] "result_pipeline_id"                          
[16] "result_status_id"                            
[17] "result_priority"                             
[18] "result_last_note"                            
[19] "result_start_date"                           
[20] "result_last_update"                          
[21] "result_num_updates"                          
[22] "result_start_status_id"                      
[23] "result_last_updated_by"                      
[24] "result_sort_order"                           
[25] "result_show_in_reports"                      
[26] "result_pipeline_item_id"                     
[27] "result_status_name"                          
[28] "success"                                     
[29] "result_custom_fields_priority"               
[30] "result_custom_fields_descripcion_oportunidad"
[31] "result_custom_fields_valor"
```

# Obtaining credentials:
In order to make the package works, you would need to create an .Renviron
file inside your working directory that should contain environment variables
as your api token, user code and pipelineID





